ICBEdataset_paper_figure_prep

### 2022-01-26 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
fixes
paper rmds

library(flextable); library(ftExtra)
library(tidyverse)
library(googlesheets4)

@@

codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_long_agreed_embeded.Rds'))

@@

codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/temp/codings_wide_agreed_embeded.Rds'))

@@

>>>>

library(flextable)
library(ftExtra)
library(tidyverse)

@@

codings_long_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/codings_long_agreed_embeded.Rds'))

@@

codings_wide_agreed_embeded %>% saveRDS(paste0(here::here(), '/replication_paper/data/temp/codings_wide_agreed_embeded.Rds'))

@@

ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_PlotInterCoderAgreement.Rmd
paper rmds

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/data/in/icb_long_clean.Rds")) 
codings_long <- readRDS(paste0(here::here(), '/replication_data/data/in/codings_long.Rds'))
codings_long_agreement <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreement.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_long_agreed.Rds'))
codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_data/data/in/codings_wide_agreed.Rds'))

>>>>

```{r}
icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds")) 
codings_long <- readRDS(paste0(here::here(), '/replication_paper/data/in/codings_long.Rds'))
codings_long_agreement <- readRDS( paste0(here::here(), '/replication_paper/data/in/codings_long_agreement.Rds'))
codings_long_agreed <- readRDS( paste0(here::here(), '/replication_paper/data/in/codings_long_agreed.Rds'))
codings_wide_agreed <- readRDS( paste0(here::here(), '/replication_paper/data/in/codings_wide_agreed.Rds'))

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_figure_prep.Rmd
paper rmds

icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/","icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds"))

@@

#child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
```

>>>>

icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds"))

@@

#child=c('ICBEdataset_paper_PlotInterCoderAgreement.Rmd')
# p_semantic_embeddings <- readRDS(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.Rds'))
# ggsave(file=paste0(here::here(), '/replication_paper/figures/p_semantic_embeddings.png'), plot = p_semantic_embeddings, width=8, height=8)
```
